A complete solution for scattering in a kind of quiver gauge theory

### 2025-04-08 Intermediate report/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage[most]{tcolorbox}
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\left\langle #1 \right\rangle}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

@@

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage[most]{tcolorbox}
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\left\langle #1 \right\rangle}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

@@

\begin{frame}
    \begin{columns}[T]
        \begin{column}{0.6\textwidth}
        \begin{itemize}
            \item 5-point
            \begin{itemize}
                \item $\bm{V_1V_1V_1V_1V_1}$
                \item $\bm{V_2V_2V_2V_2V_2}$
                \item $\bm{\Phi^\dagger V_1V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2V_2\Phi^\dagger}$
                \item $\bm{V_2\Phi^\dagger V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1}$
                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_1}$ (Not yet solved)
                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_2}$ (Not yet solved)
            \end{itemize}
        \end{itemize}
    \end{column}
    \begin{column}{0.48\textwidth}
        \begin{itemize}
            \item 6-point
            \begin{itemize}
                \item $\bm{V_1V_1V_1V_1V_1V_1}$
                \item $\bm{V_2V_2V_2V_2V_2V_2}$
                \item $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$
                \item $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$\\
                $\qquad$ $\vdots$\\
                $\qquad$ $ \vdots$
            \end{itemize}
        \end{itemize}
    \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Color structure}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke-Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies for MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item $\Phi^\dagger V_1V_1\Phi$
        \begin{figure}
            \centering
            \begin{subfigure}{0.3\textwidth}
              \includegraphics[width=\linewidth]{sch.pdf}
              \caption{s channel}
            \end{subfigure}
            \hfill
            \begin{subfigure}{0.3\textwidth}
              \includegraphics[width=\linewidth]{uch.pdf}
              \caption{u channel}
            \end{subfigure}
            \hfill
            \begin{subfigure}{0.3\textwidth}
              \includegraphics[width=\linewidth]{tch.pdf}
              \caption{t channel}
            \end{subfigure}
          \end{figure}
        The color factor can be written respectively as following
        \begin{equation*}
            r_s=\mathrm{Tr}[\Phi_2^\dagger T^{a_3}T^{a_4}\Phi_1],\,r_u=\mathrm{Tr}[\Phi_2^\dagger T^{a_4}T^{a_3}\Phi_1],\,
            r_t=\mathrm{Tr}[\Phi_2^\dagger [T^{a_3},T^{a_4}]\Phi_1]
        \end{equation*}
        We can easily obtain a similar Jacobbi relation
        \begin{equation*}
            r_t=r_s-r_u
        \end{equation*}
        Then we can accomplish the color decomposition and define the corressponding color-ordered amplitudes.
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item[] For example, in the 4pt. case, the full amplitude can be decomposed to the following form
        \begin{align*}
            \mathcal{A}_4(\Phi^\dagger V_1V_1\Phi)&=A_s r_s+A_u r_u+A_t r_t\\
            &=A_s r_s+A_u r_u+A_t(r_s-r_u)\\
            &=(A_s+A_t)r_s+(A_u-A_t)r_u
        \end{align*}
        The two subamplitudes can be defined as color-ordered amplitude with order \textcolor{red}{[1,2,3,4]} and 
        \textcolor{red}{[1,2,4,3]} respectively.

        \vspace{0.5em}
        Of course, for the type $\Phi^\dagger(nV_1)\Phi$ and $\Phi (nV_2) \Phi^\dagger$, we can do the same thing to define the color-ordered amplitudes.
        It should be noticed that the order only has the relation with the order of external gluon line.
        \begin{equation*}
            [1,2,\sigma(3),\sigma(4),\cdots,\sigma(n)]
        \end{equation*}
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item $V_2\Phi^\dagger V_1V_1\Phi$
    \end{itemize}
\end{frame}
